### 2025-09-18 paper/sec/introduction.tex
Intro title.

\section{Introduction: Transparent Documents}

Making sense of and verifying data-driven claims is hard, even when the evidence base (data sets and related
analyses) is in the public domain. Expert reviewers often struggle to evaluate empirical
claims~\citep{weber20}; paper retractions are frequently attributable to (non-fraudulent but significant)
errors in data management and analysis~\citep{hu25}. The ability of LLMs to assist with these challenges has
received considerable attention recently, for example in scientific fact-checking~\citep{abu-ahmad25} and
figure interpretation~\citep{roberts24}.

@@

\subsubsection{Target idioms of natural language}

NLP aspect of the problem is potentially a big problem space in itself. We will restrict interest to certain
idiomatic uses of natural language in making/justifying scientific claims.
Examples \ref{tab:fluid_examples}

>>>>

\section{Introduction: Transparent, Data-Driven Documents}

Making sense of and verifying data-driven claims is hard, even when the evidence base (data sets and related
analyses) is in the public domain. Expert reviewers often struggle to evaluate empirical claims without author
-supplied annotations that provide access to underlying data~\citep{weber20}; paper retractions are frequently
attributable to (non-fraudulent but significant) errors in data management and analysis~\citep{hu25}. The
ability of LLMs to assist with these challenges has received considerable attention recently, for example in
scientific fact-checking~\citep{abu-ahmad25} and figure interpretation~\citep{roberts24}.

@@

\subsection{Target idioms of natural language}

NLP aspect of the problem is potentially a big problem space in itself. We will restrict interest to certain
idiomatic uses of natural language in making/justifying scientific claims. Table~\ref{tab:fluid_examples}
